Title

### 2021-03-06 Papers/02_Sound_Compression/Compression.tex
progress on the paper

\section{Introduction} % ≅ 500 words
% ≅ 10\% of the text
% broad to specific
% show that the research question is clear, concise, and worthy of study.
% allow the reader to understand the rest of the paper without referring to previous publications on the topic
% What did you do?
% conclusions

@@

Domain specific compression algorithms and codecs exist in many areas. \textcite{2016ChenCompressing} for example, presents a scheme for compressing convolutional neural networks, while \textcite{2014CanovasLossy}, besides revising existing methods, proposes two lossy schemes for the compression of quality score data of genomic sequencing.

More recently, the work of \textcite{2019CalhounExploring}, explores the benefits of specific lossy compression algorithms in the context of checkpoints of computational simulations that are stored between simulation sessions.

Regarding sample based digital musical instruments, to the best of the authors' knowledge, no such specialized algorithms exist. Those signals, being highly uniform, offer an opportunity for compression that is not present in most general sounds and remain largely unexplored.

@@

New technologies such as 3D, immersive audio has propelled specific compression algorithms, such as the one presented in \textcite{2021HuAudio}. The renaissance of neural networks led to interesting results, such as the use of GANs as presented in \textcite{2018HuangBandwidth}.

@@

% Overview of methods
A continuous or discrete signal, as long as it is at least pseudo periodic, can be interpreted as succession of consecutive waveforms, each one representing a (pseudo) cycle of the wave. In the case of perfectly periodic signals, those waveforms are identical and we need only the definition of one waveform to characterise the whole signal.in pseudo periodic waves, On the other hand there are potentially variations between pseudo cycles, that must be accounted for. If the wave is sufficiently well behaved, as is the case with most sound arising from accoustic phenomenons, these changes can be attributed to variations in both the amplitude of the waveform and its length

Starting with an initial estimate of the waveform of the signal being processed, one can identify the pseudo cycles of a signal by convolving the estimated waveform with the signal. The process can be made computationally efficient by considering some characteristics of the wave.

@@

% Relate to other studies

@@

We compare the results of the algorithm here presented with some of the most popular codecs.

@@

The opus format was chosen, as, with the ACC and MP3, those are considered the most advanced \parencite{2019LaudeComprehensive} and popular \parencite{2018KwanObjective}

% Overview of results

% Key results in details

% Comparison with results in other works

@@

noise

>>>>

\section{Introduction} % ≅ 500 to 1000 words
% ≅ 10\% of the text
% broad to specific
% show that the research question is clear, concise, and worthy of study.
% allow the reader to understand the rest of the paper without referring to previous publications on the topic
% What did you do?
% conclusions

@@

Domain specific compression algorithms and codecs exist in many areas. \textcite{2016ChenCompressing} for example, presents a scheme for compressing convolutional neural networks, while \textcite{2014CanovasLossy}, besides revising existing methods, proposes two lossy schemes for the compression of quality score data of genomic sequencing. The use of lossy compression for wireless networks of sensors is studied in \textcite{2014ZordanPerformance}.

More recently the work of \textcite{2019CalhounExploring} explores the benefits of specific lossy compression algorithms in the context of checkpoints of computational simulations that are stored between simulation sessions.

Regarding sample based digital musical instruments, however, to the best of the authors' knowledge, no such specialized algorithms exist. Those signals, being highly uniform, offer an opportunity for compression that is not present in most general sounds and remain largely unexplored.

@@

New technologies such as 3D immersive audio has propelled specific compression algorithms, such as the one presented in \textcite{2021HuAudio}. The renaissance of neural networks led to interesting results, such as the use of GANs as presented in \textcite{2018HuangBandwidth}.

@@

% Overview of methods
A continuous or discrete signal, as long as it is at least pseudo periodic, can be interpreted as succession of consecutive waveforms, each one representing a (pseudo) cycle of the wave. In the case of perfectly periodic signals, those waveforms are identical and we need only the definition of one waveform to characterise the whole signal. While in pseudo periodic waves, On the other hand, there are potentially variations between pseudo cycles, that must be accounted for.
% Relate to other studies

This rationale of defining a signal as a series of a modified basis function is presented more formally, in the context of wavelets, in \textcite{1993SinhaLow}; in that work, however, the bases are wavelets that are obtained via filter banks applied using a pyramid algorithm. A similar approach can be found in \textcite{1998SrinivasanHigh}, where a perceptual metric is used, however.

In both works the wavelets coefficients are encoded in a dinamic dicinary. The present work adopts a more direct approach, obtaining a more accurate unique discrete basis.

If the wave is sufficiently well behaved, as is the case with most sound arising from accoustic phenomenons, the bulk of those changes can be attributed to variations in both the amplitude of the waveform and its length; One hence needs to identify an embrionary waveform, and register how it changes during the course of the pseudo cycles that comprise the whole signal.

We accomplish that via an iterative algorithm, that refines this waveform in each iteration

Starting with an initial estimate of the waveform of the signal being processed, one can identify the pseudo cycles of a signal by convolving the estimated waveform with the signal. The process can be made more efficient by considering some characteristics of the wave. For the initial waveform, for example, the algorithm presented in \textcite{2020TarjanoDigital} is used in cases where a simple sinusoid is less accurate.

@@

@@

% Overview of results
We compare the results of the algorithm here presented with some of the most widespread lossy codecs, using a variety of sound signals. The samples chosen reflect the proposed immeadiate application of the algorithm to sample based digital musical instruments, and thus consist of excerpts from notes from various instruments, as well as singing voice.

Overview of the samples 44100 etc

@@

The opus format was chosen, as, with the ACC and MP3, those are considered the most advanced \parencite{2019LaudeComprehensive} and popular \parencite{2018KwanObjective}.

% Key results in details
\subsection{Compressed file size}

\begin{table}[H]
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{c}{\textbf{Compressed size (bytes)}} \\
Sample        & Present Work & MP3   & ACC   & Opus \\
\hline
cello         & 1159         & 3357  & 3066  & 2021 \\
doublebass    & 1471         & 1845  & 1915  & 1339 \\
flute         & 16678        & 11565 & 8988  & 9342 \\
frenchhorn    & 4783         & 9189  & 7572  & 6219 \\
mezzosoprano  & 4669         & 3717  & 3237  & 2997 \\
saxophone     & 19260        & 20277 & 16307 & 12954 \\
singerbass    & 1989         & 3069  & 2747  & 2302 \\
singerfemaleA & 9125         & 8325  & 6593  & 6121 \\
singerfemaleB & 4470         & 6021  & 4773  & 4395 \\
singermale    & 694          & 1629  & 1777  & 977 \\
sopranoA      & 3747         & 3069  & 2656  & 2294 \\
sopranoB      & 2535         & 2709  & 2568  & 2021 \\
violin        & 1575         & 2709  & 2514  & 1754 \\
\hline
Average       & 5550.38	     & 5960.08	&4977.92	&4210.46

\end{tabular}
\caption{Comparison of the average errors of the algorithm presented in this work with the most common methods of digital envelope identification. The discrete waves used were normalized between -1 and 1. The average is between the absolute value of those waves and the envelope divided by two.}
\label{table:Error_comparison}
\end{table}

\subsection{Encoding and decoding time}

While part of the discrepancy in encoding times can be attributed to the immaturity of the implementation when compared to well stablished ones like lame for mp3, the majority of the difference is generated by the wildly different approach used by the algorithm presented in this work, since it engages in a semi exaustive search of the best basis, or paseudo cycle waveform via a series of dilated convolutions.
% Comparison with results in other works

@@

The algorithm, seeking the most accurate basis, has a tendency of filtering out noise from the compressed signal. This is not always welcome in the context of sound, since, as is the case of sounds with a percussive component, noise plays an integral part in the psychoacoustics characterization of the sound.

One solution would be to parametrically reintroduce the needed noise, with an approach similar to the presented in \textcite{1998LevineSinesTransientsNoise}, for example.
